### 2025-09-29 src/appendices/appendix2.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

   Charges: A brother was under a 2.2 GPA for two consecutive semesters.

@@

   Sanctions: Recommendation for suspension, voting privileges suspended until off of academic probation.

@@

   Charges: A brother was under a 2.2 GPA for two consecutive semesters. Brother was currently on co-op.

@@

   Sanctions: Formal apology in chapter, staggard for time equal to time out of the house upon return to the house. Recommendation for suspension.

@@

   Sanctions: The brother must complete kitchen details or actively attend study tables at a rate set by the Scholarship Chair.

@@

   Sanctions: The brother was told that they should be in chapter more, and that they should create a plan with the Scholarship Chair to ensure they would be in chapter more the next semester. EC was asked to make a clearer excuse plan that also answered the questions "what constitutes an excuse?" and "what constitutes full attendance at chapter?" in order to prevent future communication issues. For this trial, sanctions were given to the accused and a request was made to EC.

>>>>

   Charges: A brother was under a 2.2 {{< var acronyms.gpa >}} for two consecutive semesters.

@@

   Sanctions: Recommendation for suspension, voting privileges suspended until off of {{< var glossary.academic-probation >}}.

@@

   Charges: A brother was under a 2.2 {{< var acronyms.gpa >}} for two consecutive semesters. Brother was currently on co-op.

@@

   Sanctions: Formal apology in chapter, {{< var glossary.staggard >}} for time equal to time out of the house upon return to the house. Recommendation for suspension.

@@

   Sanctions: The brother must complete kitchen details or actively {{< var glossary.attend >}} study tables at a rate set by the Scholarship Chair.

@@

   Sanctions: The brother was told that they should be in chapter more, and that they should create a plan with the Scholarship Chair to ensure they would be in chapter more the next semester. {{< var acronyms.ec >}} was asked to make a clearer excuse plan that also answered the questions "what constitutes an excuse?" and "what constitutes full attendance at chapter?" in order to prevent future communication issues. For this trial, sanctions were given to the accused and a request was made to {{< var acronyms.ec >}}.

### 2025-09-29 src/articles/article12.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

# Standards Board

## Preface

@@

## Purpose

@@

## Membership

@@

## Voting

@@

## At-Large Member Removal

@@

## Accusation Procedure

@@

1. If the type of hearing was determined to be a Chapter Hearing, proceed with Article XIII, Section E.

## Hearing Preparation

1. Evidence and a statement by the anonymous accuser will be distributed by the Vice President to all members of the Standards Board between twenty-four and forty-eight hours before the hearing date and time.
1. Witnesses may volunteer to speak on behalf of or against the charges.
   a. The witnesses may volunteer by giving a written message to the Vice President stating their intent to participate and their stance at least three hours before the trial.
1. Witnesses will be advised by the Vice President that they are not to discuss the hearing or the accusation outside of the hearing.
1. Witnesses must remain outside the room until called by the Vice President and leave when dismissed.
1. The dress at the hearing will be informal.
1. The Vice President will call the hearing to order and ask all but the directly related participants to leave the room. The directly related participants are the members of Standards Board as defined in Article XII, Section C, Item 2 and the accused.

## Hearing Method

@@

## Sanctions

@@

## Appeals

@@

## Academic Review

>>>>

# Standards Board {#sec-art-IHXJUPV0}

## Preface {#sec-art-22W5QO3O}

@@

## Purpose {#sec-art-W45W9VZK}

@@

## Membership {#sec-art-31029HI0}

@@

## Voting {#sec-art-1U1T2P1X}

@@

## At-Large Member Removal {#sec-art-D83OGG9V}

@@

## Accusation Procedure {#sec-art-1D0EJQ7H}

@@

1. If the type of hearing was determined to be a Chapter Hearing, proceed with @sec-art-1B4EQ2H6.

## Hearing Preparation {#sec-art-HEKXL782}

1. Evidence and a statement by the anonymous accuser will be distributed by the Vice President to all members of the Standards Board between twenty-four and forty-eight hours before the hearing date and time.
1. Witnesses may volunteer to speak on behalf of or against the charges.
   a. The witnesses may volunteer by giving a written message to the Vice President stating their intent to participate and their stance at least three hours before the trial.
1. Witnesses will be advised by the Vice President that they are not to discuss the hearing or the accusation outside of the hearing.
1. Witnesses must remain outside the room until called by the Vice President and leave when dismissed.
1. The dress at the hearing will be informal.
1. The Vice President will call the hearing to order and ask all but the directly related participants to leave the room. The directly related participants are the members of Standards Board as defined in @sec-art-31029HI0C, Item 2 and the accused.

## Hearing Method {#sec-art-L96ICVPJ}

@@

## Sanctions {#sec-art-S2YKROAM}

@@

## Appeals {#sec-art-EM09V7RF}

@@

## Academic Review {#sec-art-HL5IIDEQ}

### 2025-09-29 src/articles/article3.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

# Chapter Meetings

## Time

@@

## Excuses

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with Article III, Section B, Item 1) will count as an unexcused absence.

## Absences

@@

## Rules and Regulations

>>>>

# Chapter Meetings {#sec-art-R50R4PX6}

## Time {#sec-art-386EGZU4}

@@

## Excuses {#sec-art-H23EB4B2}

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with @sec-art-H23EB4B2, Item 1) will count as an unexcused absence.

## Absences {#sec-art-BUK07FVL}

@@

## Rules and Regulations {#sec-art-8XE7XCGC}

### 2025-09-29 src/articles/article7.qmd
Add dark theme and fix article linking (#1)
* Fix glossary

* add scripts and fix extension

* fix article linking

# Housing Policies

## Alcohol, Tobacco, and Illegal Substances

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in Article VII, Section A, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates Article VII, Section A, Item 1, Article VII, Section A, Item 2, Article VII, Section A, Item 3, or Article VII, Section A, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. Article VII, Section A, Item 1, Article VII, Section A, Item 2, and Article VII, Section A, Item 3 will become null and void upon the downfall of Western Civilization.

## Housing Eligibility

@@

1. Brothers in violation of Article VII, Section B, Item 1 or Article VII, Section B, Item 2 are to be brought up for standards by the Vice President with the possibility of suspension.

@@

1. Brothers living in the house must have a signed housing contract by the due date (Article V, Section D, Item 5l).

@@

## Room Assignments

@@

   a. If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
      i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.

@@

   a. The Vice President will have penultimate authority, beneath the chapter, to assign rooms to the best of their ability in keeping with the guidelines established in Article VII, Section C, Item 4.

>>>>

# Housing Policies {#sec-art-N4XGGHCH}

## Alcohol, Tobacco, and Illegal Substances {#sec-art-6GSVIPRZ}

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in @sec-art-6GSVIPRZ, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, @sec-art-6GSVIPRZ, Item 3, or @sec-art-6GSVIPRZ, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, and @sec-art-6GSVIPRZ, Item 3 will become null and void upon the downfall of Western Civilization.

## Housing Eligibility {#sec-art-71TPHUXH}

@@

1. Brothers in violation of @sec-art-71TPHUXH, Item 1 or @sec-art-71TPHUXH, Item 2 are to be brought up for standards by the Vice President with the possibility of suspension.

@@

1. Brothers living in the house must have a signed housing contract by the due date (@sec-art-YZW2AQAI, Item 5l).

@@

## Room Assignments {#sec-art-C89656BJ}

@@

   a. If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
      i. Brothers listed in @sec-art-71TPHUXH, Item 2 cannot be forced to live out of the house.

@@

   a. The Vice President will have penultimate authority, beneath the chapter, to assign rooms to the best of their ability in keeping with the guidelines established in @sec-art-C89656BJ, Item 4.
